### 2014-12-13 paper.tex
Rephrase the suggestion to have commissions

  We also propose that states revise their policy on allowing state legislatures to draw lines independently.  Nonpartisan and balanced partisan processes create fair, consensus plans, as they will require agreements that prevent the parties from simply passing a partisan bill designed to reduce the prevalence of partisan gerrymandering.

>>>>

  Of course, ideally plans would not make it to the level of being invalidated by a court.  While incorporating partisan bias metrics into law would be difficult since they require real election data, compactness metrics could be integrated into the redistricting process.  Better yet, we suggest that states revise their policy on allowing state legislatures to draw lines independently.  Nonpartisan and balanced partisan processes create fair, consensus plans, as they will require agreements that prevent the parties from simply passing a partisan bill designed to reduce the prevalence of partisan gerrymandering.
